KidsAIR initial PM data work

### 2019-12-23 sums_data_cleaning.Rmd
New SUMs data cleaning RMD

---
title: "KidsAIR initial PM data work"
author: "Ethan Walker"
date: "Started 19 Nov 2019, Updated 20 Dec 2019"
output: pdf_document
---

@@

# Initial load, format, and save KidsAIR Dusttrak data
## Files here are in 3 formats: csv (2 different formats) and txt
## I had to do some manual cleaning of the files to get them named
## consistently and in reasonably similar formats to be able to load
## into R in batches, as seen below. The files I upload in the code below
## will also be uploaded to Box in a folder with my name.
## Box folder directory: 
```{r}
##### Read in dusttrack .txt files (from WMT) #####

# List files
list_txt_files <- list.files("Input/WMT/dusttrack_txt_files")

# Set working directory and load files in list; extract file name and add as column
## run next 6 lines together
setwd("Input/WMT/dusttrack_txt_files")
initial_data = tibble(file_list = list_txt_files) %>%
  extract(file_list, "home_winter_id", remove = FALSE) %>%
  mutate(save_data = lapply(file_list, read_csv, skip = 28)) %>%
  unnest(save_data) %>%
  select(-file_list)

# Format combined file from above; combine with other PM data below
wmt_pm_txt <- initial_data %>% 
  mutate(date = mdy(`MM/dd/yyyy`),
         time = `hh:mm:ss`,
         pm = as.numeric(`mg/m^3`),
         area = "WMT") %>% 
  unite("datetime", c("date", "time"), sep = " ", remove = FALSE) %>% 
  select(home_winter_id, datetime, date, time, pm, area)

##### Read in dusttrack .csv files (all areas) #####

@@

# Load Dusttrak data and do initial clean-up
```{r}
# Load full, raw dataset compiled in chunk above
kids_pm_full <- read_rds("Output/kids_pm_full_raw.rds")

# Load and combine data sheets with QAQC comments, etc
ak_dt_home <- read_csv("Input/AK/ak_dt_home.csv") %>% 
  mutate(area = "AK")
ak_dt <- read_xlsx("Input/AK/ak_dustrak.xlsx") %>% 
  mutate(area = "AK") %>% 
  rename_all(tolower) %>% 
  select(homewinterid, dtid, area, startdate, starttime, stopdate, stoptime)
nn_dt_home <- read_csv("Input/NN/nn_dt_home.csv") %>% 
  mutate(area = "NN")
nn_dt <- read_xlsx("Input/NN/nn_dustrak.xlsx") %>% 
  mutate(area = "NN") %>% 
  rename_all(tolower) %>% 
  select(homewinterid, dtid, area, startdate, starttime, stopdate, stoptime)
wmt_dt_home <- read_csv("Input/WMT/wmt_dt_home.csv") %>% 
  mutate(area = "WMT")
wmt_dt <- read_xlsx("Input/WMT/wmt_dustrak.xlsx") %>% 
  mutate(area = "WMT") %>% 
  rename_all(tolower) %>% 
  select(homewinterid, dtid, area, startdate, starttime, stopdate, stoptime)

dt <- rbind(ak_dt, nn_dt, wmt_dt) %>% 
  mutate(home_winter_id = as.character(homewinterid)) %>% 
  select(-homewinterid)

dt_home <- rbind(ak_dt_home, nn_dt_home, wmt_dt_home) %>% 
  rename_all(tolower) %>% 
  filter(!is.na(homewinterid)) %>% 
  mutate(home_winter_id = as.character(homewinterid)) %>% 
  select(-homewinterid) %>% 
  left_join(dt, by = c("area", "home_winter_id"))

# Join dt_home with full dataset
kids_pm_joined <- kids_pm_full %>% 
  left_join(dt_home, by = c("area", "home_winter_id")) %>% 
  rename(treatment = condition)

##### Add to new variables to Kids PM data #####
kids_pm_new <- kids_pm_joined %>%  
  #filter(area == "AK") %>% 
  # apply correction factor to pm and change to ug
  mutate(pm = pm/1.65,
         pm = pm*1000) %>% 
  mutate(home_winter_id = as.character(home_winter_id),
         area = as.factor(area),
         pm_date = date,
         pm_time = time,
         pm = as.numeric(pm),
         day_of_week = weekdays(date)) %>% 
  unite("pm_datetime", date:time, sep = " ") %>% 
  #select(home_winter_id, area, pm_date, pm_time, pm_datetime, day_of_week, pm) %>% 
  arrange(area, home_winter_id, pm_date) %>% 
  group_by(area, home_winter_id) %>% 
  # new variables summarizing pm2.5 within each home_winter_id
  mutate(pm_total_observations = n(),
         # new datetime values to calculate sampling interval
         min_datetime = first(pm_datetime),
         max_datetime = last(pm_datetime),
         min_datetime = ymd_hms(min_datetime),
         max_datetime = ymd_hms(max_datetime),
         diff_datetime = interval(min_datetime, max_datetime),
         # total sampling interval, based on first and last datetimes
         pm_sample_interval = diff_datetime/86400,
         # expected number of observations with the sampling interval
         expected_obs = pm_sample_interval*24*60,
         # difference between actual and expected observations
         actual_vs_expected_diff = pm_total_observations - expected_obs,
         # indicator variable if actual vs expected obs > 10 or greater
         actual_vs_expected = if_else(actual_vs_expected_diff < 10 &
                                      actual_vs_expected_diff > -10, 1, 0),
         pm_mean = mean(pm),
         # breaking sampling period into days
         obs = row_number(),
         sampling_day = if_else(obs < 1441, 1, 0),
         sampling_day = if_else(obs < 2881 & obs > 1440, 2, sampling_day),
         sampling_day = if_else(obs < 4321 & obs > 2880, 3, sampling_day),
         sampling_day = if_else(obs < 5761 & obs > 4320, 4, sampling_day),
         sampling_day = if_else(obs < 7201 & obs > 5760, 5, sampling_day),
         sampling_day = if_else(obs < 8641 & obs > 7200, 6, sampling_day),
         sampling_day = if_else(obs < 10081 & obs > 8640, 7, sampling_day),
         sampling_day = if_else(obs > 10080, 8, sampling_day)) %>%
  # calculate pm means for each sampling day
  group_by(area, home_winter_id, sampling_day) %>% 
  mutate(pm_mean_daily = mean(pm),
         pm_sampling_day = sampling_day) %>% 
  separate(starttime, c("trash1", "starttime"), sep = " ") %>% 
  separate(stoptime, c("trash2", "stoptime"), sep = " ") %>% 
  ungroup() %>% 
  select(-min_datetime, -max_datetime, -diff_datetime, -obs, -sampling_day, 
         -datetime, -trash1, -trash2)

# Save pm dataset as RDS and CSV
#write_rds(kids_pm_new, "Output/kids_pm_new.rds")
#write_csv(kids_pm_new, "Output/kids_pm_new.csv")
```

# Summarize by ID and Dusttrak ID to look for trends
```{r}
# Load data
kids_pm <- read_rds("Output/kids_pm_new.rds")

# summary by home_winter_id
summary_id <- kids_pm %>% 
  group_by(area, home_winter_id) %>% 
  summarise("n" = n(),
            "Mean PM" = mean(pm, na.rm = TRUE), 
            "SD PM" = sd(pm, na.rm = TRUE),
            "Min PM" = min(pm, na.rm = TRUE), 
            "Median PM" = median(pm, na.rm = TRUE),
            "Max PM" = max(pm, na.rm = TRUE),
            "Act vs Exp Diff" = first(as.numeric(actual_vs_expected_diff)),
            "Act vs Exp" = first(actual_vs_expected),
            "Comments" = first(qaqccomments))
 write_csv(summary_id, "output/kids_summary_id.csv")

# summary by dusttrak id
summary_dtid <- kids_pm %>% 
  group_by(dtid) %>% 
  summarise("n" = n(),
            "Mean PM" = mean(pm, na.rm = TRUE), 
            "SD PM" = sd(pm, na.rm = TRUE),
            "Min PM" = min(pm, na.rm = TRUE), 
            "Median PM" = median(pm, na.rm = TRUE),
            "Max PM" = max(pm, na.rm = TRUE))
```

# Histogram for distribution of PM by individual ID
```{r}
# Load data
kids_pm <- read_rds("Output/kids_pm_new.rds")

histogram_id <- kids_pm %>% 
  filter(home_winter_id == "10" & area == "AK") %>% 
  ggplot() + 
    geom_histogram(aes(pm), bins = 50) +
    theme_classic()
histogram_id
```

# Function to look at PM data across time
```{r}
# Plot PM by datetime to look at trends, gaps, and peaks
pm_time_plot_function <- function(id, location) {
pm_time_plot <- kids_pm %>% 
  filter(home_winter_id == id & area == location) %>% 
  #filter(pm < 30000) %>% 
  arrange(pm_datetime) %>% 
  mutate(pm_sampling_day = as.character(pm_sampling_day),
         day_of_week = factor(day_of_week,
                              levels = c("Sunday", "Monday", "Tuesday", "Wednesday", 
                                         "Thursday", "Friday", "Saturday"))) %>%
  ggplot() + 
    geom_point(aes(pm_datetime, pm, color = day_of_week), size = 1.5) +
    theme_classic() +
    labs(title = id,
         y = expression(paste("PM"[2.5], " (", mu, g/m^3, ")")),
         x = "Datetime",
         color = "Day of week") +
    theme(axis.title.y = element_text(size = 12,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.title.x = element_text(size = 12),
          axis.text.x = element_blank(),
          axis.text.y = element_text(size = 12, color = "black"),
          axis.line.x = element_line(colour = "black", size = 1), 
          axis.line.y = element_line(colour = "black", size = 1), 
          axis.ticks = element_blank()) +
    scale_color_manual(values = jv_palette)

gaps <<- kids_pm %>% 
  filter(home_winter_id == id & area == location) %>% 
  mutate(pm_datetime = ymd_hms(pm_datetime),
         datetime_lead = ymd_hms(lead(pm_datetime)),
         datetime_1 = seconds(pm_datetime),
         datetime_2 = seconds(datetime_lead),
         datetime_diff_minutes = as.numeric(datetime_2 - datetime_1)/60,
         datetime_diff_hours = as.numeric(datetime_diff_minutes/60)) %>% 
  arrange(desc(datetime_diff_minutes)) %>% 
  select(day_of_week, pm_sampling_day, datetime_diff_minutes, datetime_diff_hours, 
         pm_datetime, datetime_lead)

pm_desc <<- kids_pm %>% 
  filter(home_winter_id == id & area == location) %>% 
  arrange(desc(pm)) %>% 
  select(pm_datetime, pm, pm_sampling_day)

pm_time_plot
}
```

# Run function from above to look at results
```{r}
# Load data
kids_pm <- read_rds("Output/kids_pm_new.rds")

# Change function input to look at specific home
# Run all of these lines together
pm_time_plot_function(id = "129", location = "WMT")
head(gaps, 25)
head(pm_desc, 25)
tail(pm_desc, 25)

# filter data for a single home
check_data <- kids_pm %>% 
  filter(area == "WMT" & home_winter_id == "129") %>% 
  filter(pm < 0)
```

# Check sample start times
```{r}
# Load data
kids_pm <- read_rds("Output/kids_pm_new.rds")

# Checking difference between dustrak start datetime and field data log datetime
sample_times <- kids_pm %>% 
  #filter(area == "AK") %>% 
  group_by(area, home_winter_id) %>% 
  arrange(pm_datetime) %>% 
  unite(start_datetime, c("startdate", "starttime"), 
        sep = " ", remove = FALSE) %>% 
  mutate(first_datetime = first(pm_datetime),
         first_datetime = ymd_hms(first_datetime),
         start_datetime = ymd_hms(start_datetime),
         time_diff = first_datetime - start_datetime) %>% 
  distinct(time_diff, .keep_all = TRUE) %>% 
  select(area, home_winter_id, pm_datetime, first_datetime,
         start_datetime, time_diff, startdate, starttime) %>% 
  ungroup() %>% 
  arrange(area, home_winter_id)
#write_csv(sample_times, "Output/pm_sample_times_comparison.csv")
```

# Loading and combining notes from time and PM logs
```{r}
time_notes <- read_xlsx("Input/pm_sample_times_comparison.xlsx") %>% 
  select(area, home_winter_id, first_datetime, start_datetime,
         time_diff, next_steps_time, check_log_time)

pm_notes <- read_xlsx("Input/kids_summary_id.xlsx") %>% 
  select(area, home_winter_id, n, further_comments_pm, next_steps_pm, check_log_pm)

kids_ids <- read_rds("Output/kids_linked_ids.rds") %>% 
  mutate(home_winter_id = as.numeric(home_winter_id))

notes_joined <- pm_notes %>% 
  left_join(time_notes, by = c("area", "home_winter_id")) %>% 
  left_join(kids_ids, by = c("area", "home_winter_id"))
#write_csv(notes_joined, "Output/pm_notes_check_logs.csv")
```

# Fix dusttrak sample start times
```{r}
# Load data
kids_pm <- read_rds("Output/kids_pm_new.rds")

# Checking difference between dustrak start datetime and field data log datetime
kids_pm_new <- kids_pm %>% 
  #filter(area == "NN") %>% 
  group_by(area, home_winter_id) %>% 
  arrange(pm_datetime) %>% 
  unite(start_datetime, c("startdate", "starttime"), 
        sep = " ", remove = FALSE) %>% 
  mutate(first_datetime = first(pm_datetime),
         first_datetime = ymd_hms(first_datetime),
         start_datetime = ymd_hms(start_datetime),
         time_diff = first_datetime - start_datetime) %>% 
  #distinct(time_diff, .keep_all = TRUE) %>% 
  # make general time changes based on ranges
  mutate(pm_datetime = ymd_hms(pm_datetime),
         pm_datetime_new = if_else(time_diff > 1800 & time_diff < 5400, 
                                   pm_datetime - 3600, pm_datetime),
         pm_datetime_new = if_else(time_diff < -1800 & time_diff > -5400, 
                                   pm_datetime_new + 3600, pm_datetime_new),
         pm_datetime_new = if_else(time_diff > 5400 & time_diff < 9000, 
                                   pm_datetime_new - 7200, pm_datetime_new),
         pm_datetime_new = if_else(time_diff < -5400 & time_diff > -9000, 
                                   pm_datetime_new + 7200, pm_datetime_new)) %>% 
  # make specific time changes
  mutate(pm_datetime_new = if_else(time_diff == 10903, # WMA457
                                   pm_datetime_new - 10800, pm_datetime_new),
         pm_datetime_new = if_else(time_diff == (-82721), # WMA440
                                   pm_datetime_new + 82800, pm_datetime_new),
         pm_datetime_new = if_else(time_diff == 10069, # WMA459
                                   pm_datetime_new - 9900, pm_datetime_new),
         pm_datetime_new = if_else(time_diff == 9817, # WMA314
                                   pm_datetime_new - 3600, pm_datetime_new),
         pm_datetime_new = if_else(time_diff < -31535900, # YKC06-103 
                                   pm_datetime_new + 31539519, pm_datetime_new),
         pm_datetime_new = if_else(time_diff < -31532200, # WMA305
                                   pm_datetime_new - 3600, pm_datetime_new),
         pm_datetime_new = if_else(time_diff == 9120, # WMA228
                                   pm_datetime_new - 3600, pm_datetime_new),
         pm_datetime_new = if_else(time_diff == (-21497), # WMA130
                                   pm_datetime_new + 21497, pm_datetime_new),
         pm_datetime_new = if_else(time_diff == 684, # WMA237
                                   pm_datetime_new + 3600, pm_datetime_new),
         pm_datetime_new = if_else(time_diff == 149793, # WMA238
                                   pm_datetime_new - 149793, pm_datetime_new),
         pm_datetime_new = if_else(time_diff == -46227, # CH320
                                   pm_datetime_new + 3600, pm_datetime_new),
         pm_datetime_new = if_else(time_diff == 13514, # TC360 
                                   pm_datetime_new - 3600, pm_datetime_new),
         pm_datetime_new = if_else(time_diff == -10696, # TC357 
                                   pm_datetime_new + 10800, pm_datetime_new),
         pm_datetime_new = if_else(time_diff == -43427, # TC355 
                                   pm_datetime_new + 43200, pm_datetime_new),
         pm_datetime_new = if_else(time_diff == -11388, # TC353 
                                   pm_datetime_new + 10800, pm_datetime_new),
         pm_datetime_new = if_else(time_diff == -221, # TC351 
                                   pm_datetime_new + 3600, pm_datetime_new),
         pm_datetime_new = if_else(time_diff == 4999, # CH214 
                                   pm_datetime_new + 3600, pm_datetime_new),
         pm_datetime_new = if_else(time_diff == 4061, # WMA203 
                                   pm_datetime_new + 3600, pm_datetime_new)) %>% 
  mutate(first_datetime_new = first(pm_datetime_new),
         first_datetime_new = ymd_hms(first_datetime_new),
         start_datetime = ymd_hms(start_datetime),
         time_diff_new = first_datetime_new - start_datetime) %>%  
  #distinct(time_diff, .keep_all = TRUE) %>%
  ungroup() %>% 
  arrange(area, home_winter_id, pm_datetime_new)

# write_rds(kids_pm_new, "Output/kids_pm_new.rds")
```

# Further cleaning:
## Remove specific homes from PM dataset
## Remove extremely high values
## Change negative values
```{r}
# Load data
kids_pm <- read_rds("Output/kids_pm_new.rds")

kids_pm_new <- kids_pm %>%
  # filtering out specific homes where PM data is not suitable for analysis
  # removes 119,520 obs
         # YKC06_105: only 12 hours of data
  mutate(do_not_use = if_else(area == "AK" & home_winter_id == "39", 1, 0),
         # YKC06_313: sample hourly instead of every minute
         do_not_use = if_else(area == "AK" & home_winter_id == "89", 1, do_not_use),
         # CH_302: sample hourly instead of every minute
         do_not_use = if_else(area == "NN" & home_winter_id == "127", 1, do_not_use),
         # CH_304: Home was resampled
         do_not_use = if_else(area == "NN" & home_winter_id == "1330", 1, do_not_use),
         # CH_306: sample hourly instead of every minute
         do_not_use = if_else(area == "NN" & home_winter_id == "134", 1, do_not_use),
         # CH_307: only 8 datapoints
         do_not_use = if_else(area == "NN" & home_winter_id == "135", 1, do_not_use),
         # TC_357: Home was resampled
         do_not_use = if_else(area == "NN" & home_winter_id == "1510", 1, do_not_use),
         # CH_322: sample hourly instead of every minute
         do_not_use = if_else(area == "NN" & home_winter_id == "161", 1, do_not_use),
         # CH_325: 6300 obs are negative, down to -12.12. Median is negative.
         do_not_use = if_else(area == "NN" & home_winter_id == "165", 1, do_not_use),
         # CH_400: Home was resampled
         do_not_use = if_else(area == "NN" & home_winter_id == "2150", 1, do_not_use),
         # CH_403: Home was resampled
         do_not_use = if_else(area == "NN" & home_winter_id == "2210", 1, do_not_use),
         # CH_108: Only 300 datapoints and no other files found
         do_not_use = if_else(area == "NN" & home_winter_id == "29", 1, do_not_use),
         # CH_207: Only 400 datapoints; no other files found
         do_not_use = if_else(area == "NN" & home_winter_id == "58", 1, do_not_use),
         # TC_230: Home was resampled
         do_not_use = if_else(area == "NN" & home_winter_id == "620", 1, do_not_use),
         # CH_223: Home was resampled
         do_not_use = if_else(area == "NN" & home_winter_id == "840", 1, do_not_use),
         # TC_242: 1 day worth of data with lots of gaps
         do_not_use = if_else(area == "NN" & home_winter_id == "86", 1, do_not_use),
         # WMA277: Home was resampled
         do_not_use = if_else(area == "WMT" & home_winter_id == "1910", 1, do_not_use),
         # WMA305: Home was resampled
         do_not_use = if_else(area == "WMT" & home_winter_id == "2500", 1, do_not_use),
         # WMA306: Home was resampled
         do_not_use = if_else(area == "WMT" & home_winter_id == "2510", 1, do_not_use),
         # WMA358: Home was resampled
         do_not_use = if_else(area == "WMT" & home_winter_id == "2860", 1, do_not_use),
         # WMA448: Home was resampled
         do_not_use = if_else(area == "WMT" & home_winter_id == "3750", 1, do_not_use),
         # WMA200: 4700 negative values, down to -4.85. Median is negative
         do_not_use = if_else(area == "WMT" & home_winter_id == "152", 1, do_not_use),
         # WMA201: 5000 negative values, down to -10. Median negative. 17 hour gap 
         do_not_use = if_else(area == "WMT" & home_winter_id == "153", 1, do_not_use),
         # WMA603: Home was resampled
         do_not_use = if_else(area == "WMT" & home_winter_id == "5100", 
                              1, do_not_use)) %>% 
  filter(do_not_use != 1) %>% 
  # replace PM > 10,000 with NA (33 obs)
  mutate(pm = if_else(pm > 10000, 999999, pm)) %>% 
  replace_with_na(replace = list(pm = 999999)) %>% 
  # replace PM < 1 (lower DustTrak limit) with 0.5 (lower limit / 2) 
  # 291,490 obs less than 1; 56,684 obs less than 0 
  mutate(pm = if_else(pm < 1, 0.5, pm))

# write_rds(kids_pm_new, "Output/kids_pm_new.rds")
```

# New variables to use for analysis
```{r}
# Load data
kids_pm <- read_rds("Output/kids_pm_new.rds")
cleaning_summary <- read_xlsx("Input/cleaning_summary.xlsx") %>% 
  select(area, home_winter_id, final_cleaning_pm, sensitivity_analysis_pm)

kids_pm_new <- kids_pm %>% 
  mutate(home_winter_id = as.numeric(home_winter_id)) %>% 
  left_join(cleaning_summary, by = c("area", "home_winter_id")) %>% 
  select(-samplingdate, -samplingtime, -pickupdate, -pickuptime,
         -dtmin, -dtmax, -dtaverage, -qaqccomments, -data_comments,
         -pm_sampling_day, -pm_mean_daily) %>% 
  # create sampling days based on datetime differences
  group_by(area, home_winter_id) %>% 
  mutate(pm_datetime_new = if_else(is.na(pm_datetime_new), 
                                   pm_datetime, pm_datetime_new),
         first_datetime_new = first(pm_datetime_new),
         first_datetime_new = ymd_hms(first_datetime_new)) %>% 
  mutate(datetime_diff = pm_datetime_new - first_datetime_new,
         sampling_day = if_else(datetime_diff <= 86400, 1, 0),
         sampling_day = if_else(datetime_diff > 86400 & datetime_diff <= 172800, 
                                2, sampling_day),
         sampling_day = if_else(datetime_diff > 172800 & datetime_diff <= 259200, 
                                3, sampling_day),
         sampling_day = if_else(datetime_diff > 259200 & datetime_diff <= 345600, 
                                4, sampling_day),
         sampling_day = if_else(datetime_diff > 345600 & datetime_diff <= 432000, 
                                5, sampling_day),
         sampling_day = if_else(datetime_diff > 432000 & datetime_diff <= 518400, 
                                6, sampling_day),
         sampling_day = if_else(datetime_diff > 518400 & datetime_diff <= 604800, 
                                7, sampling_day),
         sampling_day = if_else(datetime_diff > 604800 & datetime_diff <= 691200, 
                                8, sampling_day),
         sampling_day = if_else(datetime_diff > 691200 & datetime_diff <= 777600, 
                                9, sampling_day),
         sampling_day = if_else(datetime_diff > 777600 & datetime_diff <= 864000, 
                                10, sampling_day),
         sampling_day = if_else(datetime_diff > 864000, 
                                11, sampling_day)) %>% 
  # new vars for daily means and % expected observations for each day
  group_by(area, home_winter_id, sampling_day) %>% 
  mutate(pm_mean_daily = mean(pm),
         percent_daily_obs_pm = n()/1440) %>% 
  ungroup() %>% 
  arrange(area, home_winter_id, pm_datetime_new) %>% 
  select(-first_datetime, -time_diff, -do_not_use)

test <- kids_pm_new %>% 
  filter(percent_daily_obs_pm >= 0.9) %>% 
  summarise(n()/2241695)
# write_rds(kids_pm_new, "Output/kids_pm_new.rds")
# write_csv(kids_pm_new, "Output/kids_pm_new.csv")
```

>>>>

---
title: "KidsAIR initial PM data work"
author: "Ethan Walker"
date: "Started 23 Dec 2019, Updated 23 Dec 2019"
output: pdf_document
---

@@

```{r}
wmt_sums_data_log <- read_csv("Input/WMT/wmt_sums_data_log.csv") %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         date = ChangeDate,
         time = ChangeTime,
         alarms = Alarms,
         file_name = ibutFile,
         notes = `REPLACE(REPLACE(Notes`) %>% 
  select(home_winter_id, date, time, alarms, file_name, notes)

kids_linked_ids <- read_rds("Output/kids_linked_ids.rds") %>% 
  filter(area == "WMT") %>% 
  select(home_winter_id, home)

wmt_sums_log <- wmt_sums_data_log %>% 
  left_join(kids_linked_ids, by = "home_winter_id") %>% 
  select(home_winter_id, home, date, time, alarms, file_name, notes)

write_csv(wmt_sums_log, "Output/wmt_sums_data_log.csv")
```

# Initial load, format, and save KidsAIR Dusttrak data
## Files here are in 3 formats: csv (2 different formats) and txt
## I had to do some manual cleaning of the files to get them named
## consistently and in reasonably similar formats to be able to load
## into R in batches, as seen below. The files I upload in the code below
## will also be uploaded to Box in a folder with my name.
## Box folder directory: 
```{r}
##### Read in sums csv files (from WMT) #####

# List files
list_csv_files <- list.files("Input/WMT/sums_csv_new")

# Set working directory and load files in list; extract file name and add as column
## run next 12 lines together
setwd("Input/WMT/sums_csv_new")
initial_data = tibble(file_list = list_csv_files) %>%
  extract(file_list, "home", remove = FALSE) %>%
  mutate(save_data = lapply(file_list, read_csv, skip = 1,
                            col_names = c("line", "date", "time", "temp_c", "trash"),
                            col_types = cols(line = col_double(),
                                             date = col_date(format = ""),
                                             time = col_time(format = ""),
                                             temp_c = col_character(),
                                             trash = col_character()))) %>%
  unnest(save_data) %>%
  select(-file_list)

# Format combined file from above; combine with other PM data below
wmt_sums_csv <- initial_data %>% 
  mutate(area = "WMT",
         home2 = "WMA") %>% 
  unite("datetime", c("date", "time"), sep = " ", remove = FALSE) %>% 
  unite("home", c("home2", "home"), sep = "") %>% 
  mutate(datetime_sums = datetime,
         date_sums = date,
         time_sums = time,
         temp_c_sums = temp_c) %>% 
  select(home, area, datetime_sums, date_sums, time_sums, temp_c_sums)

# List files
list_csv_files_2 <- list.files("Input/WMT/sums_csv_old/format_1")

# Set working directory and load files in list; extract file name and add as column
## run next 7 lines together
setwd("Input/WMT/sums_csv_old/format_1")
initial_data = tibble(file_list = list_csv_files_2) %>%
  extract(file_list, "home", remove = FALSE) %>%
  mutate(save_data = lapply(file_list, read_csv, skip = 22,
                            col_names = c("datetime_sums", "temp_c_sums"))) %>%
  unnest(save_data) %>%
  select(-file_list)

# Format combined file from above; combine with other PM data below
wmt_sums_csv_2 <- initial_data %>% 
  mutate(area = "WMT",
         home2 = "WMA",
         datetime_sums = ymd_hms(datetime_sums)) %>% 
  separate("datetime_sums", c("date_sums", "time_sums"), sep = " ", remove = FALSE) %>% 
  unite("home", c("home2", "home"), sep = "") %>% 
  mutate(date_sums = ymd(date_sums)) %>% 
  select(home, area, datetime_sums, date_sums, time_sums, temp_c_sums) %>% 
  na.exclude()

# List files
list_csv_files_3 <- list.files("Input/WMT/sums_csv_old/format_2")

# Set working directory and load files in list; extract file name and add as column
## run next 12 lines together
setwd("Input/WMT/sums_csv_old/format_2")
initial_data = tibble(file_list = list_csv_files_3) %>%
  extract(file_list, "home", remove = FALSE) %>%
  mutate(save_data = lapply(file_list, read_csv, skip = 2,
                            col_names = c("line", "date", "time", "temp_f", "trash"),
                            col_types = cols(line = col_double(),
                                             date = col_character(),
                                             time = col_time(format = ""),
                                             temp_f = col_double(),
                                             trash = col_character()))) %>%
  unnest(save_data) %>%
  select(-file_list)

# Format combined file from above; combine with other PM data below
wmt_sums_csv_3 <- initial_data %>% 
  mutate(area = "WMT",
         home2 = "WMA") %>% 
  unite("datetime", c("date", "time"), sep = " ", remove = FALSE) %>% 
  unite("home", c("home2", "home"), sep = "") %>% 
  mutate(datetime_sums = mdy_hms(datetime),
         date_sums = mdy(date),
         time_sums = time,
         temp_c_sums = (temp_f-32)/1.8) %>% 
  select(home, area, datetime_sums, date_sums, time_sums, temp_c_sums)

##### Read in sums csv files (from WMT) #####

# List files
list_csv_files <- list.files("Input/WMT/sums_xlsx_files")

# Set working directory and load files in list; extract file name and add as column
## run next 12 lines together
setwd("Input/WMT/sums_xlsx_files")
initial_data = tibble(file_list = list_csv_files) %>%
  extract(file_list, "home", remove = FALSE) %>%
  mutate(save_data = lapply(file_list, read_csv, skip = 1,
                            col_names = c("line", "date", "time", "temp_c", "trash"),
                            col_types = cols(line = col_double(),
                                             date = col_date(format = ""),
                                             time = col_time(format = ""),
                                             temp_c = col_character(),
                                             trash = col_character()))) %>%
  unnest(save_data) %>%
  select(-file_list)

# Format combined file from above; combine with other PM data below
wmt_sums_csv <- initial_data %>% 
  mutate(area = "WMT",
         home2 = "WMA") %>% 
  unite("datetime", c("date", "time"), sep = " ", remove = FALSE) %>% 
  unite("home", c("home2", "home"), sep = "") %>% 
  mutate(datetime_sums = datetime,
         date_sums = date,
         time_sums = time,
         temp_c_sums = temp_c) %>% 
  select(home, area, datetime_sums, date_sums, time_sums, temp_c_sums)
```

# Code from PM cleaning
```{r}
##### Read in dusttrack .csv files (all areas) #####

@@
